---
title: "Analysis of Weight Lifting Exercise Classification"
author: "Iqbal Abdillah Suwandi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This report presents an analysis of the Weight Lifting Exercise dataset using machine learning techniques. The goal is to classify how participants perform barbell lifts based on sensor data collected from accelerometers placed on their belt, forearm, arm, and dumbbell. The target variable, classe, represents different exercise types.

#Load Libraries
```{r}
library(tidyverse)     
library(caret)         
library(randomForest)  
library(rpart)         
library(rpart.plot)   
library(e1071) 
```

#Load Data
```{r}
# Define URLs
train_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
test_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

# Load data
train_data <- read.csv(url(train_url), na.strings = c("NA", ""))
test_data <- read.csv(url(test_url), na.strings = c("NA", ""))
```

#Data Cleaning & Preprocessing
```{r}
# Remove columns with too many missing values
train_data <- train_data[, colSums(is.na(train_data)) == 0]
test_data <- test_data[, colSums(is.na(test_data)) == 0]

# Remove irrelevant coloms
train_data <- train_data[, -c(1:7)]
test_data <- test_data[, -c(1:7)]

# Convert class to factor
train_data$classe <- as.factor(train_data$classe)
```

#Split Data for Training & Validation
```{r}
set.seed(123)
trainIndex <- createDataPartition(train_data$classe, p = 0.7, list = FALSE)

# Create training and validation sets
trainSet <- train_data[trainIndex, ]
validationSet <- train_data[-trainIndex, ]
```

#Train the Machine Learning Model
```{r}
set.seed(123)
model_rf <- randomForest(classe ~ ., data = trainSet, importance = TRUE, ntree = 100)
```

#Model Evaluation
```{r}
predictions <- predict(model_rf, validationSet)
conf_matrix <- confusionMatrix(predictions, validationSet$classe)
print(conf_matrix)
```

#Features Importance
```{r}
varImpPlot(model_rf)
```

#Apply MOdel to Test Data
```{r}
final_predictions <- predict(model_rf, test_data)
print(final_predictions)
```

#Prediciton
```{r}
pml_write_files = function(x) {
  for(i in 1:length(x)) {
    filename = paste0("problem_id_", i, ".txt")
    write.table(x[i], file = filename, quote = FALSE, row.names = FALSE, col.names = FALSE)
  }
}
pml_write_files(final_predictions)
```


This analysis successfully classified weightlifting exercises using sensor data. The Random Forest model demonstrated high accuracy, and key sensor readings were identified as important predictors.